Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-04 manuscript.tex
5 updates

\jessi{The next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
The correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters. This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything. This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).

@@

In Fig \ref{fig:alphacent:correctionRV}, we study the efficiency of the stellar activity correction proposed in Sec.~\ref{sec:31}. The first observation we can make is that the RV measured with SN mean RV presents a rms 35\% larger than the RV measured when fitting a Normal density. In the case of SN median RV, we see as well a larger RV rms, however only 9\% larger. Even though we see those differences in RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, we find the same RV residuals rms. 
%In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
Therefore, although it seems that the parameters derived using the SN density are more sensitive to stellar activity, we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.

>>>>

\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
The correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters. This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything. This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).

@@

\jessi{I changed some things in the following paragraph that I'm not completely sure are accurate - please review}
\jessi{The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
The RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
the remaining std of the residuals are essentially the same for all three approaches.
%In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
Although it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the N density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
%we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.
}
